---
title: "Problem set 1"
author: "Minglan YE"
date: "02/03/2019"
output:
  html_document:
    df_print: paged
---



# Details

- Who did you collaborate with: Bala
- Approximately how much time did you spend on this problem set: 4 hours
- What, if anything, gave you the most trouble: 


# Task 1

Yes, I have watched the short videos you mentioned on the Task 1. 


# Task 2

## Life expectancy in 2007

```{r load-packages, warning=FALSE, message=FALSE}
# Notice the warning=FALSE and message=FALSE in the chunk options. R spits out 
# a lot of messages when you load tidyverse and we don't want those in the 
# final document.

library(tidyverse) 
# This loads ggplot2, dplyr, and other packages you'll need
library(gapminder)  # This loads the gapminder data
```

Let's first look at the first few rows of data:

```{r view-data}
head(gapminder)
```

Right now, the `gapminder` data frame contains rows for all years for all countries. We want to only look at 2007, so we create a new data frame that filters only rows for 2007.

Note how there's a weird sequence of characters: `%>%`. This is called a *pipe* and lets you chain functions together. We could have also written this as `gapminder_2007 <- filter(gapminder, year == 2007)`.

```{r filter-2007}
gapminder_2007 <- gapminder %>%
  filter(year == 2007)

head(gapminder_2007)
```

Now we can plot a histogram of 2007 life expectancies with the default settings:

```{r plot-2007-1}
ggplot(data = gapminder_2007, 
       mapping = aes(x = lifeExp)) +
  geom_histogram()
```

R will use 30 histogram bins by default, but that's not always appropriate, and it will yell at you for doing so. **Adjust the number of bins to 2, then 40, then 100.** **What's a good number for this data? Why?**

TYPE YOUR ANSWER HERE.

I thinke the best number of bins should be 40 since X-axis is showing the age of life.

```{r plot-2007-2}
ggplot(data = gapminder_2007, 
       mapping = aes(x = lifeExp)) +
  geom_histogram(bins = 100)
```

## Average life expectancy in 2007 by continent

We're also interested in the differences of life expectancy across continents. First, we can group all rows by continent and calculate the mean

This is where the `%>%` function is actually super useful. Remember that it lets you chain functions together—this means we can read these commands as a set of instructions: take the `gapminder` data frame, filter it, group it by continent, and summarize each group by calculating the mean. Without using the `%>%`, we could write this same chain like this: `summarize(group_by(filter(gapminder, year == 2007), continent), avg_life_exp = mean(lifeExp))`. But that's *awful* and impossible to read and full of parentheses that can easily be mismatched.

```{r calc-mean}
gapminder_cont_2007 <- gapminder %>%
  filter(year == 2007) %>% 
  group_by(continent) %>%
  summarize(avg_life_exp = mean(lifeExp))

head(gapminder_cont_2007)
```

Let's plot these averages as a bar chart:

```{r plot-2007-bar}
ggplot(data = gapminder_cont_2007, 
       mapping = aes(x = continent, y = avg_life_exp, fill = continent)) + 
  geom_col()
```

Then, let's plot them as density distributions. We don't need to use the summarized data frame for this, just the original filtered `gapminder_2007` data frame:

```{r plot-2007-density}
ggplot(data = gapminder_2007, 
       mapping = aes(x = lifeExp, fill = continent)) + 
  geom_density()
```

Now let's plot life expectancies as violin charts. These are the density distributions turned sideways:

```{r plot-2007-violin}
ggplot(data = gapminder_2007, 
       mapping = aes(x = continent, y = lifeExp, fill = continent)) + 
  geom_violin()
```

Finally, we can add actual points of data for each country to the violin chart:

```{r plot-2007-violin-points}
ggplot(data = gapminder_2007, 
       mapping = aes(x = continent, y = lifeExp, fill = continent)) + 
  geom_violin() +
  geom_point()
```

The bar chart, density plot, violin plot, and violin plot + points each show different ways of looking at a single number—the average life expectancy in each continent. **Answer these questions:**

- Which plot is most helpful? TYPE YOUR ANSWER HERE.
  I think the violin plot with points are most helpful one by helping me to visualize the spread of lifeExp and common age for lifeexp for each continets. 
  
- Which ones show variability? TYPE YOUR ANSWER HERE.
  I think the violin with point show more variablities. 
  
- What's going on with Oceania? TYPE YOUR ANSWER HERE.
  Oceania has the longest lifeexp.

# Task 3: R and ggplot

```{r load-libraries-1, warning=FALSE, message=FALSE}
# Technically you don't need to run this because we loaded tidyverse earlier in Task 2
library(tidyverse)
```


## 3.2.4

**1: Run `ggplot(data = mpg)`. What do you see?**

```{r blank-plot, fig.width=2, fig.height=2}
ggplot(data = mpg)
```

TYPE YOUR ANSWER HERE. (hint: I gave you the answer in the chunk name)

blank plot. ggplot(data=mpg) is the dataset to use in the grpah.

(Notice how I used `fig.width` and `fig.height` in the chunk options. You can click on the little gear icon in the far left of the chunk to change other options.)

**2: How many rows are in `mpg`? How many columns?**

A data frame with 234 rows and 11 variables.

```{r mpg-details}
nrow(mpg)
ncol(mpg)

# Or
dim(mpg)

# Or
mpg
```

**3: What does the `drv` variable describe? Read the help for `?mpg` to find out.**

 f= front-wheel drive, r = rear wheel drive, 4 = 4wd

**4: Make a scatterplot of `hwy` vs `cyl`.**

```{r hwy-cyl-scatterplot}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = hwy, y = cyl))

```

**5: What happens if you make a scatterplot of `class` vs `drv`? Why is the plot not useful?**

```{r class-drv-scatterplot}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = class, y = drv), position = 'jitter')
```

the plot will not be helpful because not all the data are shown in the graph due to overlapping. Adding jitter to show that the overlapping problem.

## 3.3.1

Q1 
we need to put the color on the outside to apply for geom_point. 

```{r displ-hwy-scatterplot-blue}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy),color = "blue")
```

Q2
run the data frame in the mgp then under each column it will show <CHR> means catergorical variables. <dbl> and <int> menas continous variable. (Also can find in the 3.2.1 The mpg Dataframe.)

```{r dataframe of mpg}
ggplot2::mpg
```

Q3
```{r ggplot color}
ggplot(data=mpg) + 
    geom_point(mapping = aes(x=displ, y=hwy, color=cty))
```

```{r ggplot size}
ggplot(data=mpg) + 
    geom_point(mapping = aes(x=displ, y=hwy, size=cty))
```

```{ggplot shape}
ggplot(data=mpg) + 
    geom_point(mapping = aes(x=displ, y=hwy, shape=cty))
```

we cant run shape on a continous variables. we can only run shape into catogorical variables and only 6 different catogorical can be catogorized.  

Q4

It will show both size and color on the graph and create two different legends.

```{r multiple aesthetics}
ggplot(data=mpg)+
  geom_point(mapping = aes(x=displ, y=hwy, color=cty, size=cty))
```

Q5
Stroke is used for modify the width of the boarder.
```{r}
?geom_point
```

## 3.5.1

```{Q1}
What happens if you facet on a continuous variable?

R will produce each graph for each variable. no comparsion between the variables which not presenting anything to the viewers. If there are tons of variables, there will be tons of graph. It's too much graph for viewer to see at one time. 
```

Q2
```{r Q2}
ggplot(data=mpg)+
  geom_point(mapping=aes(x=drv,y=cyl))
```

```{r Q2 with facet_grid}
ggplot(data=mpg)+
  geom_point(mapping=aes(x=drv,y=cyl)) +
  facet_grid(drv~cyl)
```

I think the empty cell means there is no data in the mpg. 

Q3

. means not facet in the rows or columns dimension.

Q4

If we use color, there will be too many dots in the graph and will be hard for viewer to visualize the data. By spliting the data into individual graph, helps better visualization. But facet the data into dividual grpahy makes harder to compare the overall relationship with other variables. 

## 3.6.1

Q1
What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

line - geom_line()
boxplot - geom_boxplot()
histogram - geom_histogram()
area chart - geom_area()

Q2
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

Q3
show.legend=false will removes the legend. if remove the legend, it will be hard for viewer to know what color represent what data.

```{r legend}
ggplot(data = mpg) +
  geom_smooth(
    mapping = aes(x = displ, y = hwy, color = drv),
    show.legend = FALSE)
```

Q4
it determines if there should be draw the confident interval around the line or not.

Q5
two graphys looks the same. if the mpg data didnt change, the graphy will be the same since same data and same geom settings.


## 3.8.1

Q1
If we do it with the geom_point, r will gather the similiar point togehter which will cause overlapping problem.
```{r Q1 improve the graph}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter()
```

Q2
width and height.